Assignment 4

### 2015-03-09 rmtw/a4/latex8.tex
Changes have been made!

\subsection{There is no difference in efficiency}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.

\subsection{There is no difference in effectiveness}
The same test was chosen for Hrate, based on the same reasoning. The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.

>>>>

\subsection{There is no difference in efficiency}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.

\subsection{There is no difference in effectiveness}
The same test was chosen for Hrate, based on the same reasoning. The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.
